Precise predictions for same-sign W-boson scattering at the LHC

### 2018-02-28 Draft/scanLO.tex
fixed the comments in sections 4 and 5 and add some discussions in the comparison
Commented about the MC errors of fig.4,7

In Fig.~\ref{fig:ratio2d_LO}, ratios of double-differential cross sections in the plane $\left(m_{\Pj\Pj}, \Delta y_{\Pj\Pj}\right)$ is shown.
Two plots are displayed: the ratios of the $|t|^2 + |u|^2$ and $|s|^2 + |t|^2 + |u|^2$ approximations over the full calculation.
In the first case, the approximation is good within $\pm10\%$ over the whole range apart in the low invariant-mass region at both low and large rapidity difference.
The low rapidity difference region possesses remnants of the tri-bosons contributions that peak at di-jet invariant mass around the W-boson mass.
It is therefore expected that the $|t|^2 + |u|^2$ approximation fails in this region.
The second plot, where the $|s|^2 + |t|^2 + |u|^2$ approximation is considered, displays a better behaviour in the previously mentioned region.
The full calculation is approximated at the level of $\pm5\%$ apart in the region where $\Delta y_{\Pj\Pj} < 2$.
\AK{What are the MC error on these plots?}
\MP{@AK: I changed some stuffs in the text to justify the plot range}

>>>>

In Fig.~\ref{fig:ratio2d_LO}, ratios of double-differential cross sections in the plane $\left(m_{\Pj\Pj}, \Delta y_{\Pj\Pj}\right)$ is shown.
Two plots are displayed: the ratios of the $|t|^2 + |u|^2$ and $|s|^2 + |t|^2 + |u|^2$ approximations over the full calculation.
In the first case, the approximation is good within $\pm10\%$ over the whole range apart in the low invariant-mass region at both low and large rapidity difference.
The low rapidity difference region possesses remnants of the tri-bosons contributions that peak at di-jet invariant mass around the W-boson mass.
It is therefore expected that the $|t|^2 + |u|^2$ approximation fails in this region.
The second plot, where the $|s|^2 + |t|^2 + |u|^2$ approximation is considered, displays a better behaviour in the previously mentioned region.
The full calculation is approximated at the level of $\pm5\%$ apart in the region where $\Delta y_{\Pj\Pj} < 2$.
\AK{What are the MC error on these plots?} \GP{It would be hard to show them on the plot: I have uploaded the MC errors of each bin in th edirectory SCAN, both for fig.4 (LO) and fig.7 (NLO).}
